---
title: "Lab 3 Report"
author: Nathan Snell
date: "`r format(Sys.Date())`"
output: github_document
---

Instructions for this lab report can be found on [Your assignment section of Lab Assignment 3 Introduction to ggplot2](https://biol275-msum.github.io/introduction-to-ggplot2.html#your-assignment) on the lab website.

## Fireflies
> A. Insert an R code chunk and create a graph depicting the frequency distribution of the 35 mass measurements. It should have legible text and appropriate axis labels.

ggplot(data = Fireflies_data) +
  geom_histogram(mapping = aes(x = spermatophoreMass), binwidth = .008,
                 fill = "#C5351B", color = "black") +
  labs(x = "Spermatophore Mass", y = "Frequency (number of males)") +
  scale_y_continuous(breaks = seq(0, 7.5, 2.5), limits = c(0, 7.5))+ 
  scale_x_continuous(breaks = seq(0, 0.15, .03)) +
  theme_classic() +
  theme(
    axis.title = element_text(face = "bold"))



> B. What type of graph did you choose in part (A)? Why?

I chose a histogram because the firefly data was a distribution of a single numerical variable.


> C. Describe the shape of the frequency distribution. What are its main features?

The shape of the frequency distribution looks like that of a bell curve. This means the highest number of males producing a particular spermatophore mass is in the middle. As the curve exits the middle, it falls lower and lower on both sides.


> D. What term would be used to describe the largest measurement in the frequency distribution? You can refer to the lecture slides, your notes, or the textbook.

The term to describe the largest measurement in the frequency distribution is the mode. 


## Bird orders

I read the data using the code provided by the instructor. The dataset is from the auk package and was originally named ebird_taxonomy. I converted it to a tibble, removed non-species taxa, and named the new dataset birds.

```{r}

```

> E. How many bird species are in the new birds dataset? How did you find out?

There are 10,721 species in the dataset. I found this out by making the table and looking at the number of observations. Since each observation is a species, then the number of observations is the number of species.


> H. How many orders are there? You can get this right by counting on the graph, but you will only get full points if you use some code to figure it out.

There are 41 orders in this data set. Running the distinct function of the birds data and specifying the order gives you a tibble of the number of orders there are. The code used is provided below.

distinct(birds, order)


> F. Insert an R code chunk and create a graph depicting the distribution of orders in the birds dataset. Sort the orders with the most frequent on the left. It should have legible text and appropriate axis labels.

ggplot(birds)+
  geom_bar(mapping = aes(x =fct_infreq(order)))+ 
  labs(x ="Order", y ="Frequency (Number of Species)")+
  scale_y_log10()+  
  theme(
    axis.text = element_text(color = "black"),
    axis.text.x = element_text(angle = 60, hjust = 1))

> G. What kind of graph did you create? Why?

I created a bar graph because we wanted to show and order a single categorical set of data.


## Links to peer review

I reviewed Tyler Edvall's lab report at this URL:  

https://github.com/BIOL275-MSUM/lab-3-intro-to-ggplot-tdedvall/blob/9cd5211526b0caa957b93f8d82f3b7d8b71ea373/README.md 

Johnathan Kanyinda reviewed my lab report at this URL: 

https://github.com/BIOL275-MSUM/lab-3-intro-to-ggplot-NathanSnell1

## Session Info

Here is my session information:

```{r}
sessioninfo::session_info()
```
